draft_final_assignment

### 2022-11-28 draft_final_assingment.Rmd
cleaning_file

---
title: "junk_final_assignment"
author: "Andrew Wells"
date: "11/18/2022"
output: html_document
---

@@

```{r}
url <- "https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/dummy_df.csv"

df <- read_csv(url)
```

## Cleaning data
```{r}
#Trying to extract party name (D or R) from the sponsor, will figure this out with Regex

df$Party <- ifelse(str_detect(df$Sponsor, "R-[A-Z]{2,}"),"Republican", ifelse(str_detect(df$Sponsor,"D-[A-Z]{2,}"),"Democrat", NA))
```

## Creating a corpus
```{r}
df_corp <- df
df_corp <- df_corp %>% rename(text = Summary)
corp <- corpus(df_corp)

````

##Creatung a dfm from the corpus
```{r}
dfm_corp <- corp %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm()

````

>>>>

---
title: "draft_final_assignment"
author: "Andrew Wells"
date: "11/18/2022"
output: html_document
---

@@

```{r }
df <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_11_28.csv")
```
## Creating a corpus
```{r }
df_corp <- df
df_corp <- df_corp %>% rename(text = summary)
corp <- corpus(df_corp)
```

##Creatung a dfm from the corpus
```{r }
dfm_corp <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used"))%>%
  dfm()
```
